A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by organization x.}

### 2021-09-02 paper.tex
Tables Update
Experiment Config & Result Tables

@@

@@

@@

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{bib/bibliografia.bib}
%
\end{document}

>>>>

    \begin{table}[]
        \begin{tabular}{|l|l|}
        \hline
        \multicolumn{2}{|l|}{OneMax   (DEAP)} \\ \hline
        Population & 60 \\ \hline
        Max   Generation & 20 \\ \hline
        Stagnation & Off \\ \hline
        Chromosome   Length & 20 \\ \hline
        Target   Fitness & 20 \\ \hline
        Crossover   Rate & 100 \\ \hline
        Mutation   Rate & 7 \\ \hline
        Tourney   Reprod. Rate & 50 \\ \hline
        Tourney   Sample & 3 \\ \hline
        \end{tabular}
        \end{table}

    \begin{table}[]
        \begin{tabular}{|l|l|}
        \hline
        \multicolumn{2}{|l|}{LifeCycle   Algorithm} \\ \hline
        Population & 60 \\ \hline
        Max   Generation & 20 \\ \hline
        Stagnation & Off \\ \hline
        Chromosome   Length & 20 \\ \hline
        Target   Fitness & 20 \\ \hline
        Crossover   Rate & 100 \\ \hline
        Mutation   Rate & 7 \\ \hline
        Tourney   Reprod. Rate & 50 \\ \hline
        Tourney   Sample & 4 \\ \hline
        Max   Age & 80 \\ \hline
        Open   Reprod. Rate & 5 \\ \hline
        Closed   Reprod. Rate & 45 \\ \hline
        Fertility   Rate & 100 \\ \hline
        Base   Approval & 80 \\ \hline
        Goal   Approval & 100 \\ \hline
        Max   Wait Time & 2 \\ \hline
        \end{tabular}
        \end{table}

@@

    \begin{table}[]
        \begin{tabular}{|l|l|l|l|l|}
        \hline
        \multicolumn{5}{|c|}{\textbf{OneMax DEAP}} \\ \hline
        \begin{tabular}[c]{@{}l@{}}Run   \\    \\ No.\end{tabular} & Generation & \begin{tabular}[c]{@{}l@{}}Best \\    \\ Individual\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total\\    \\ Evaluations\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total Time \\    \\ (seconds)\end{tabular} \\ \hline
        1 & 6 & 20 & 360 & 0.016 \\ \hline
        2 & 5 & 20 & 300 & 0.032 \\ \hline
        3 & 7 & 20 & 420 & 0.061 \\ \hline
        4 & 9 & 20 & 540 & 0.081 \\ \hline
        5 & 8 & 20 & 480 & 0.080 \\ \hline
        6 & 6 & 20 & 360 & 0.062 \\ \hline
        7 & 7 & 20 & 420 & 0.062 \\ \hline
        8 & 6 & 20 & 360 & 0.016 \\ \hline
        9 & 8 & 20 & 480 & 0.058 \\ \hline
        10 & 6 & 20 & 360 & 0.050 \\ \hline
        11 & 7 & 20 & 420 & 0.073 \\ \hline
        12 & 8 & 20 & 480 & 0.076 \\ \hline
        13 & 8 & 20 & 480 & 0.065 \\ \hline
        14 & 6 & 20 & 360 & 0.060 \\ \hline
        15 & 6 & 20 & 360 & 0.045 \\ \hline
        16 & 6 & 20 & 360 & 0.059 \\ \hline
        17 & 6 & 20 & 360 & 0.061 \\ \hline
        18 & 6 & 20 & 360 & 0.058 \\ \hline
        19 & 5 & 20 & 300 & 0.060 \\ \hline
        20 & 7 & 20 & 420 & 0.067 \\ \hline
        21 & 7 & 20 & 420 & 0.060 \\ \hline
        22 & 7 & 20 & 420 & 0.085 \\ \hline
        23 & 7 & 20 & 420 & 0.071 \\ \hline
        24 & 4 & 20 & 300 & 0.049 \\ \hline
        25 & 6 & 20 & 360 & 0.050 \\ \hline
        26 & 9 & 20 & 540 & 0.081 \\ \hline
        27 & 6 & 20 & 420 & 0.074 \\ \hline
        28 & 6 & 20 & 360 & 0.064 \\ \hline
        29 & 6 & 20 & 360 & 0.065 \\ \hline
        30 & 4 & 20 & 240 & 0.016 \\ \hline
        Avg. & 6.5 & 20 & 394 & 0.059 \\ \hline
        \end{tabular}
        \end{table}

    \begin{table}[]
        \begin{tabular}{|l|l|l|l|l|}
        \hline
        \multicolumn{5}{|c|}{\textbf{LifeCycle Algorithm}} \\ \hline
        \begin{tabular}[c]{@{}l@{}}Run   \\    \\ No.\end{tabular} & Generation & \begin{tabular}[c]{@{}l@{}}Best \\    \\ Individual\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total\\    \\ Evaluations\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total Time \\    \\ (seconds)\end{tabular} \\ \hline
        1 & 8 & 20 & 486 & 6.65 \\ \hline
        2 & 6 & 20 & 381 & 5.20 \\ \hline
        3 & 6 & 20 & 369 & 5.69 \\ \hline
        4 & 7 & 20 & 434 & 6.37 \\ \hline
        5 & 12 & 20 & 731 & 8.20 \\ \hline
        6 & 5 & 20 & 306 & 4.55 \\ \hline
        7 & 13 & 20 & 764 & 8.34 \\ \hline
        8 & 4 & 20 & 233 & 4.09 \\ \hline
        9 & 12 & 20 & 692 & 7.27 \\ \hline
        10 & 6 & 20 & 338 & 4.76 \\ \hline
        11 & 9 & 20 & 559 & 7.78 \\ \hline
        12 & 12 & 20 & 730 & 8.35 \\ \hline
        13 & 4 & 20 & 219 & 3.43 \\ \hline
        14 & 8 & 20 & 462 & 5.28 \\ \hline
        15 & 4 & 20 & 217 & 3.37 \\ \hline
        16 & 4 & 20 & 234 & 4.54 \\ \hline
        17 & 4 & 20 & 256 & 4.35 \\ \hline
        18 & 12 & 20 & 714 & 8.14 \\ \hline
        19 & 12 & 20 & 694 & 7.88 \\ \hline
        20 & 15 & 20 & 892 & 9.74 \\ \hline
        21 & 11 & 20 & 633 & 7.98 \\ \hline
        22 & 3 & 20 & 169 & 4.02 \\ \hline
        23 & 10 & 20 & 611 & 6.89 \\ \hline
        24 & 10 & 20 & 629 & 7.32 \\ \hline
        25 & 7 & 20 & 416 & 6.22 \\ \hline
        26 & 7 & 20 & 446 & 5.55 \\ \hline
        27 & 6 & 20 & 379 & 5.95 \\ \hline
        28 & 8 & 20 & 466 & 6.98 \\ \hline
        29 & 3 & 20 & 197 & 3.36 \\ \hline
        30 & 6 & 20 & 381 & 6.16 \\ \hline
        Avg. & 7.8 & 20 & 468 & 6.15 \\ \hline
        \end{tabular}
        \end{table}

@@

\section{Ignored Elements}

@@

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{bib/bibliografia.bib}
%
\end{document}
